Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-06 07-discussion.tex
Semi-finalized dynamic limits section, which finally completes the whole design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@865 df1a90cd-247b-4364-bdaf-287a704eb499

In section ~\ref{sec:interest flooding} we made assumptions regarding the Interest flooding traffic shape (requesting non-existing data with non-aggregatable prefix name ) and single-path forwarding strategy, which jointly create the most powerful congestion at the producer link.

In this paper we are using a simple attacker profile Ñ greedy attacker, which is using all resources (available bandwidth) of its botnet in order to put producer down as quickly as possible. However, in a real life not all botnets are greedy and in fact can perform smart actions like constant switching between victims every other hour to fool defensive systems by nullifying gathered bad flow statistics. Or they can be non-greedy at all, for instance a large botnet of several hundreds of thousands nodes can perform a non-greedy attack by sending just a few Interests per second from each node. Nowadays, this situation is very hard to manage, because of the difficulties in detecting of bad flows in a traffic.

>>>>

In section~\ref{sec:interest flooding} we made assumptions regarding the Interest flooding traffic shape (requesting non-existing data with non-aggregatable prefix name ) and single-path forwarding strategy, which jointly create the most powerful congestion at the producer link.

In this paper we are using a simple attacker profile and greedy attacker, which is using all resources (available bandwidth) of its botnet in order to put producer down as quickly as possible. However, in a real life not all botnets are greedy and in fact can perform smart actions like constant switching between victims every other hour to fool defensive systems by nullifying gathered bad flow statistics. Or they can be non-greedy at all, for instance a large botnet of several hundreds of thousands nodes can perform a non-greedy attack by sending just a few Interests per second from each node. Nowadays, this situation is very hard to manage, because of the difficulties in detecting of bad flows in a traffic.

### 2012-12-06 algos/probabilistic.tex
Semi-finalized dynamic limits section, which finally completes the whole design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@865 df1a90cd-247b-4364-bdaf-287a704eb499

A main drawback of the probabilistic Interests accept method is the fact that each router on the path make an independent decision on what to do with the Interest.
As a result of such independent decisions, the probability of legitimate Interests not to be dropped quickly decreases as the number of hops between the requester and Data grows, worsening the satisfaction statistics and resulting in further drops of the Interests.
In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
At the same time, the router B sees the satisfaction rate for its \texttt{eth0} interface at 30\%.
Next time a legitimate Interests arrives on the router A, it has 50\% chance to be forwarded further, and if forwarded, it has only $50\% \times 30\% = 15\%$ chance to be actually send towards the Data producer.
To prevent such overreacting, we need to enable some form of a gossiping protocol between neighboring NDN routers, in order to explicitly specify amount of Interests that each router is willing to forward.

>>>>

A main drawback of the probabilistic Interests accept method is the fact that each router on the path make an independent decision on what to do with the Interest.
As a result of such independent decisions, the probability of legitimate Interests not to be dropped decreases quickly as the number of hops between the requester and Data grows, worsening the satisfaction statistics and resulting in further drops.
In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
At the same time, the router B sees the satisfaction rate for its \texttt{eth0} interface at 30\% level.
Next time a legitimate Interests arrives on the router A, it has 50\% chance to be forwarded further, and if forwarded, it has only $50\% \times 30\% = 15\%$ chance to be actually send towards the Data producer.
To prevent such overreacting, we need to enable some form of a gossiping protocol between neighboring NDN routers, in order to explicitly specify amount of Interests that each router is willing to forward.
